---
title: "Survey_Data_Analysis"
author: "Tingjun"
output: 
  html_document:
    highlight: tango
    toc_depth: 3 
    number_sections: true 
    theme: journal
    toc: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# 1 Load Packages
```{r}
# Data Manipulation
library(readxl)
library(tidyverse)
# Data Visualisation
library(sjPlot) #Data Visualization for Statistics in Social Science
library(huxtable) # A package for creating text tables https://hughjonesd.github.io/huxtable/huxtable.html
library(gtsummary) # provides an elegant and flexible way to create publication-ready analytical and summary tables. https://www.danieldsjoberg.com/gtsummary/
library(flextable) # provides a framework for easily create tables for reporting and publications. https://ardata-fr.github.io/flextable-book/
library(hrbrthemes)
library(viridis)
library(ggpubr)
library(report)

# Data Analysis
library(rstatix) #Pipe-Friendly Framework for Basic Statistical Tests
library(survey)  # Analysis of Complex Survey Samples https://www.rdocumentation.org/packages/survey/versions/4.1-1
library(jtools) # This is a collection of tools for more efficiently understanding and sharing the results of (primarily) regression analyses https://cran.r-project.org/web/packages/jtools/vignettes/summ.html
library(psych) # https://www.rdocumentation.org/packages/psych/versions/2.2.5
library(afex)
library(qacDR) # https://rkabacoff.github.io/factorAnalysis/articles/factorAnalysis.html

# Linear mixed effect model
library(lme4) 

# post-hoc test in LMM
library(emmeans) 
library(lmerTest)

```

## 1.1 Data Manipulation

Extract, rename and combine the variables to produce the final dataset. 
 
```{r}

# Data cleaning
dat <- read_xlsx("data.xlsx")


temp0 <- dat %>% mutate(BFNE = BFNE_1 + BFNE_2 + BFNE_3 + BFNE_4 + BFNE_5 + BFNE_6 +
                               BFNE_7 + BFNE_8 + BFNE_9 + BFNE_10 + BFNE_11 + BFNE_12,
                        PRCS = PRCS_1 + PRCS_2 + PRCS_3 + PRCS_4 + PRCS_5 + PRCS_6 +
                               PRCS_7 + PRCS_8 + PRCS_9 + PRCS_10 + PRCS_11 + PRCS_12,
                        SSPS = SSPSN_1 + SSPSN_2 + SSPSN_3 + SSPSN_4 + SSPSN_5)

temp1 <- temp0 %>% select(Subject,Gender,Employment,Age,Education,
                          LargeNeutralAudience_Classroom,MediumNeutralAudience_Classroom, SmallNeutralAudience_Classroom,
                          LargeDisengagedAudience_Classroom,LargeEngagedAudience_Classroom,
                          MediumDisengagedAudience_Classroom,
                          MediumEngagedAudience_Classroom,SmallDisengagedAudience_Classroom,SmallEngagedAudience_Classroom,
                          LargeDisengagedAudience_Lecture,LargeEngagedAudience_Lecture,
                          MediumDisengagedAudience_Lecture,MediumEngagedAudience_Lecture,
                          SmallDisengagedAudience_Lecture,
                          SmallEngagedAudience_Lecture,LargeDisengagedAudience_InterviewRoom,
                          LargeEngagedAudience_InterviewRoom,
                          MediumDisengagedAudience_InterviewRoom,MediumEngagedAudience_InterviewRoom,
                          SmallDisengagedAudience_InterviewRoom,
                          SmallEngagedAudience_InterviewRoom,LargeNeutralAudience_Lecture,
                          MediumNeutralAudience_Lecture,
                          SmallNeutralAudience_Lecture,LargeNeutralAudience_InterviewRoom,MediumNeutralAudience_InterviewRoom,
                          SmallNeutralAudience_InterviewRoom,BFNE,PRCS,SSPS)

SurveyData <- temp1 %>% gather(key=var1, value="Score",- Subject, - Gender,- Employment,- Age, - Education,
                               - BFNE, - PRCS, - SSPS)                                              %>%     
                        mutate(Roomsize=ifelse(grepl("Class",var1),"Classroom", 
                                               ifelse(grepl("Lecture",var1),"Lecture","InterviewRoom")))  %>%
                        mutate(Audiencesize=ifelse(grepl("Large",var1),"Large", 
                                                   ifelse(grepl("Medium",var1),"Medium","Small")))  %>% 
                        mutate(Valence=ifelse(grepl("Engaged",var1),"Engaged",
                                              ifelse(grepl("Disengaged",var1),"Disengaged","Neutral")))        %>%
                        mutate(Roomsize=as.factor(Roomsize), Audiencesize=as.factor(Audiencesize), 
                               Valence=as.factor(Valence))                                          %>% 
                        select(-var1)

SurveyData <- as.tibble(SurveyData)

# Re-level factors
SurveyData$Roomsize <- factor(SurveyData$Roomsize, levels = c("InterviewRoom", "Classroom", "Lecture"))

SurveyData$Valence <- factor(SurveyData$Valence, levels = c("Disengaged", "Neutral", "Engaged"))

SurveyData$Audiencesize <- factor(SurveyData$Audiencesize, levels = c("Small", "Medium", "Large"))

```



# 2 Mixed Effect Anova

First set the default coding scheme to "sum" so that Type III tests are correctly calculated.
```{r}
options(contrasts=c("contr.sum","contr.poly"))
```

## 2.1 LMEM model

Fit the full factorial model of Audience x Room x Valence for the anxiety scores. With subject as the random factor as we have no repeats per-subject within each cell.

```{r}
mod.1 <- lmer(Score ~ Audiencesize * Roomsize * Valence + (1|Subject), data = SurveyData)
summary(mod.1)
```

### 2.1.1 Testing for Normality Assumption

```{r}
# Compute Shapiro-Wilk test for each combinations of factor levels
SurveyData %>%
  group_by(Audiencesize, Valence, Roomsize) %>%
  shapiro_test(Score)

# Create QQ plot for each cell of design
ggqqplot(SurveyData, "Score", ggtheme = theme_bw()) +
  facet_grid(Audiencesize + Valence ~ Roomsize, labeller = "label_both")

# Homogneity of variance assumption
## Compute the Levene’s test after grouping the data by Audiencesize and Valence categories
SurveyData %>%
  group_by(Audiencesize, Valence) %>%
  levene_test(Score ~ Roomsize)
```

### 2.1.2 Descriptive stats
```{r}
Survey_desc <- SurveyData %>% select(Age, Gender, Education, Employment)
tbl_desc <- tbl_summary(Survey_desc)
tbl_desc
```


## 2.2 Three-way interaction

### 2.2.1 Visualising the 3-way interaction

```{r}
# Bar plot
g0 <- ggplot(SurveyData, aes(Valence, Score, fill = Audiencesize)) +
            facet_wrap(~ Roomsize)

g1 <- g0 + stat_summary(fun = mean, geom = "bar", position = "dodge", stat = "identity")

# boxplot
bxp <- ggboxplot(
  SurveyData, x = "Valence", y = "Score",
  color = "Audiencesize", palette = "grey",
  facet.by = "Roomsize", short.panel.labs = FALSE
  )

# Annotate
g2 <-  g1 + labs(x="Audience Engagement", y = "Anxiety Level", 
       fill ="Audience Size") +
       theme_ipsum() +
       scale_fill_grey(start = 0.40, end = 0.6)

# model interaction
g_inter <-emmip(mod.1, Audiencesize ~ Valence | Roomsize, CIs=T)

# Print
g2
g_inter
bxp
```

### 2.2.2 Three-way interaction
```{r}

three_way <- anova(mod.1, type=3)
get_anova_table(three_way)
```

Mixed effect Anova demonstrated that there was a significant three-way interaction between room size, audience size, and audience engagement, p < 0.001

### 2.2.3 Simple two-way interaction by Roomsize

```{r}
two_way <- joint_tests(mod.1, by = "Roomsize", adjust="holm")
two_way
```
A two-way interaction between audience engagement * audience size was found in the interview room (p < .005) and classroom (p < .001) settings.

### 2.2.4 Simple Mian Effects

For both `Roomsize = Interview Room` and `Roomsize = Classroom` and , we need to breakdown the `Valence x Audiencesize` interaction. 
#### Two way
```{r}
emm.twoway <- as.data.frame(joint_tests(mod.1, by = c("Audiencesize","Roomsize"), p.adjust="holm"))
emm.twoway[-7:-9, ]
```
For the `Roomsize = Interview Room`, only the large audience size was associated with anxiety scores that differed depending upon audience engagement condition, whereas both medium and small showed no effect of audience engagement condition.

For the `Roomsize = Classroom`, the effect was opposite as the small and medium audience sizes led to a difference in anxiety scores across the different valences, whereas the large audience size showed no effect of audience engagement condition.

### 2.2.5 Simple Simple Mian Effects
```{r}
# Interview room
emm.final <- emmeans(mod.1, pairwise ~ Valence|Audiencesize:Roomsize, adjust="holm")
emm.interview <- emm.final$contrasts[7:9,]
emm.interview
```
When participants were presented in the `interview room`, the large, disengaged audience led to significantly lower anxiety scores than either neutral (p < .001) or positively engaged condition (p = .008) (Fig 3. Interview room panel).

#### Classroom
```{r}
emm.classroom <-emm.final$contrasts[10:15,]
emm.classroom
```
In the classroom scenario, the effect of audience engagement at a small audience size was driven by both the disengaged (p = 0.004) and neutral (p < 0.001) conditions producing significantly smaller anxiety scores than the positively engaged condition. When audience size was medium, significantly lower anxiety scores were seen for the disengaged audience than either neutral (p = 0.006) or positively engaged (p = 0.001) (Fig 3. Classroom panel).


Testing the levels of `Audiencesize` within `Roomsize=Lecture` reveals
```{r}
emm.lecture <- emmeans(mod.1, pairwise ~ Audiencesize | Roomsize, adjust="holm")
emm.lecture$contrasts[7:9]
```

In the lecture scenario, the perceived anxiety score significantly increased as the audience size increased (p < 0.001


# 3 Factor Analysis
## 3.1 Principle axis factor
### 3.1.1 Data
```{r}
paf_data<- temp1 %>% 
           select(LargeNeutralAudience_Classroom,MediumNeutralAudience_Classroom,    
                  SmallNeutralAudience_Classroom,LargeDisengagedAudience_Classroom,
                  LargeEngagedAudience_Classroom,MediumDisengagedAudience_Classroom,
                  MediumEngagedAudience_Classroom,SmallDisengagedAudience_Classroom,
                  SmallEngagedAudience_Classroom,LargeDisengagedAudience_Lecture,
                  LargeEngagedAudience_Lecture,MediumDisengagedAudience_Lecture,
                  SmallEngagedAudience_Lecture,LargeDisengagedAudience_InterviewRoom,
                  LargeEngagedAudience_InterviewRoom,
                  MediumDisengagedAudience_InterviewRoom,MediumEngagedAudience_InterviewRoom,
                  SmallDisengagedAudience_InterviewRoom,
                  SmallEngagedAudience_InterviewRoom,LargeNeutralAudience_Lecture,
                  MediumNeutralAudience_Lecture,
                  SmallNeutralAudience_Lecture,LargeNeutralAudience_InterviewRoom,
                  MediumNeutralAudience_InterviewRoom,SmallNeutralAudience_InterviewRoom)

KMO(paf_data)
```
### 3.1.2 Screeplot
```{r}
scree_plot(paf_data)
```
## 3.2 Principle Axis Factor
```{r}
fit.fa <- FA(paf_data, nfactor=3, rotate="varimax", fm="pa")
paf<-fa(paf_data,nfactors = 3,rotate="varimax",fm="pa",score=T)
```

## 3.2.1 Diagram

```{r}
fa.diagram(paf,simple = TRUE)
fa.bar <- plot(fit.fa, sort=TRUE) # plot factor pattern as bar chart
fa.bar

# add the component scores to the original data.
regr_dat <- SurveyData
regr_dat <- score(regr_dat, fit.fa)
head(regr_dat)
```
## 4 Multiregression

```{r}
# Subset participants into high & low anxiety measure

regr_h <- regr_dat[which(regr_dat$PRCS > 6), ]
regr_l <- regr_dat[which(regr_dat$PRCS <= 6), ]


fit.1<- lm(Score ~ F1 + F2 + F3 + Age + Gender + Employment + Education + BFNE + PRCS + SSPS,data = regr_dat)
fit.h <- lm(Score ~ F1 + F2 + F3 + Age + Gender + Employment + Education + BFNE + PRCS + SSPS, data = regr_h)
fit.l <- lm(Score ~ F1 + F2 + F3 + Age + Gender + Employment + Education + BFNE + PRCS + SSPS, data = regr_l)
summ(fit.1)
summ(fit.h)
summ(fit.l)

vif(model.regr)
## AIC 
model.regr <- step(fit.1)
summ(model.regr)

#report 
report_table(model.regr) 

```

```


